Proposed Solution

### 2017-01-24 CAV17/secs/eval.tex
fix table 1, wrong order

\begin{table}[h]
\centering
\caption{Results of \app}
\label{table:learning}
\setlength{\tabcolsep}{0.5em}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Class of Error } & {\bf \# Rules Learned} & {\bf \# Errors Detected} & {\bf Support} & {\bf Confidence}\\ 
\hline
\hline
Order        & 13  & 389  &  & \\ 
Missing      & 53  & 237  &  & \\ 
Type         & 92  & 1367 &  & \\ 
Fine-Grain   & 327 & 55   &  & \\ 
Coarse-Grain & 97  & 63   &  & \\ 
\hline 
\end{tabular}
\end{table}

@@

\begin{table}[h]
\centering
\caption{Time for training over various training set sizes}
\label{table:training}
\setlength{\tabcolsep}{1em}
\begin{tabular}{|c|c|c|}
\hline
{\bf \# of Files for Training} & {\bf ConfigC (sec)} & {\bf \app (sec)}\\ 
\hline
\hline
0    & 0.051    & 0.51  \\ \hline
50   & 1.815    & 1.638  \\ \hline
100  & 13.331   & 4.119  \\ \hline
150  & 95.547   & 4.231  \\ \hline
200  & 192.882  & 12.271  \\ \hline
256  & 766.904  & 15.627  \\ 
\hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h]
\centering
\caption{Results of \app}
\label{table:learning}
\setlength{\tabcolsep}{0.5em}
\begin{tabular}{|c|c|c|c|c|}
\hline
{\bf Class of Error } & {\bf \# Rules Learned} & {\bf \# Errors Detected} & {\bf Support (\%)} & {\bf Confidence (\%)}\\ 
\hline
\hline
Order        & 13  & 62   & 6 & 94 \\ 
Missing      & 53  & 55   & 2  & 71 \\ 
Type         & 92  & 389  & -  & -  \\ 
Fine-Grain   & 327 & 1367 & 24 & 91 \\ 
Coarse-Grain & 97  & 237  & 10 & 96\\ 
\hline 
\end{tabular}
\end{table}

@@

\begin{table}[h]
\centering
\caption{Time for training over various training set sizes}
\label{table:training}
\setlength{\tabcolsep}{1em}
\begin{tabular}{|c|c|c|}
\hline
{\bf \# of Files for Training} & {\bf ConfigC (sec)} & {\bf \app (sec)}\\ 
\hline
\hline
0    & 0.051    & 0.051  \\ \hline
50   & 1.815    & 1.638  \\ \hline
100  & 13.331   & 4.119  \\ \hline
150  & 95.547   & 4.231  \\ \hline
200  & 192.882  & 12.271  \\ \hline
256  & 766.904  & 15.627  \\ 
\hline
\end{tabular}
\end{table}
